Realistically Interesting Domains for Probabilistic Planners

### 2014-04-08 FinalPaper/paper.tex
rewrote ff replan

For a planner to be succesfull in finite-horizon MDPs they need to be scalable and sensitive to an expected reward maximization, the evaluation criteria of these domains. This caused for  LRTDP planners to emerge.

>>>>

For a planner to be succesfull in finite-horizon MDPs it needs to be scalable and sensitive to an expected reward maximization, the evaluation criteria of these domains. This caused for  LRTDP planners to emerge.
